Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
rewrite section 3

\newcommand{\vm}{\mbf{m}}
\newcommand{\vz}{\mbf{z}}
\newcommand{\vf}{\mbf{f}}
\newcommand{\vu}{\mbf{u}}
\newcommand{\vx}{\mbf{x}}
\newcommand{\vy}{\mbf{y}}
\newcommand{\vw}{\mbf{w}}

@@

>>>>

\newcommand{\vm}{\mbf{m}}
\newcommand{\vz}{\mbf{z}}
\newcommand{\vf}{\mbf{f}}
\newcommand{\vu}{\mbf{u}}
\newcommand{\vx}{\mbf{x}}
\newcommand{\vy}{\mbf{y}}
\newcommand{\vw}{\mbf{w}}
\newcommand{\va}{\mbf{a}}

@@

An alternative view of the dual variables is that they parameterize approximate likelihoods as was shown in \citep{adam2021dual} we can rewrite the GP posterior in terms of the following approximate normal distributions:
\begin{equation}
 q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\hat{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\tilde{\vy} - \vu)^\top\tilde{\MSigma}^{-1}(\tilde{\vy} - \vu)}  
\end{equation}
The first normals are the marginal likelihoods were $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$  wtih $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the prior is determined by the kernel matrix. To arrive at the MVN Gaussian we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix]. Performing conjugate summation of prior and likelihood we would arrive at the sparse GP posterior at the inducing points $\MZ$. The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables
